Apache Flink\texttrademark: Unified Stream and Batch Processing \\ in a Single Engine

### 2015-11-27 exec-model.tex
small change in fault tolerance

Recovery from failures reverts all operator states to their respective states taken from the last successful snapshot, and restarts the input streams starting from the latest barrier. The maximum amount of re-computation needed upon recovery is limited to the amount of input records between two consecutive barriers. Furthermore,  we note that this strategy does not eliminate the possibility for partial recovery, when upstream backup is applied.

>>>>

Recovery from failures reverts all operator states to their respective states taken from the last successful snapshot, and restarts the input streams starting from the latest barrier. The maximum amount of re-computation needed upon recovery is limited to the amount of input records between two consecutive barriers. Furthermore, partial recovery of a failed subtask is possible by additionally replaying unprocessed records  buffered at the immediate upstream subtasks \cite{carbone2015lightweight}.

### 2015-11-27 paper.tex
small change in fault tolerance

\section{Conclusion}
\label{sec:conclusions}
In this paper we presented Apache Flink, a platform that implements one universal dataflow engine designed to perform both stream and batch analytics. Flink's dataflow engine treats operator state and logical intermediate results as first class citizens, and is used by the batch and a data stream APIs. The streaming API that is built on top of  Flink's streaming dataflow engine, provides the means to keep recoverable state, and to partition, transform, discretize and aggregate a data stream. While batch computations are, in theory, a special case of a streaming computations, Flink treats them specially, by optimizing their execution with a novel query optimizer, and by implementing blocking operators that gracefully spill to disk in the absence of memory. 
{
\small
\bibliographystyle{abbrv}
\bibliography{references}
}
\end{document}

>>>>

\section{Conclusion}
\label{sec:conclusions}
In this paper we presented Apache Flink, a platform that implements a universal dataflow engine designed to perform both stream and batch analytics. Flink's dataflow engine treats operator state and logical intermediate results as first class citizens, and is used by both the batch and a data stream APIs, with different parameters. The streaming API that is built on top of  Flink's streaming dataflow engine, provides the means to keep recoverable state and to partition, transform, and aggregate windows of a data stream. While batch computations are, in theory, a special case of a streaming computations, Flink treats them specially, by optimizing their execution with a novel query optimizer, and by implementing blocking operators that gracefully spill to disk in the absence of memory. 
{
\small
\bibliographystyle{abbrv}
\bibliography{references}
}
\end{document}
